\newglossaryentry{ac:AGB}{
name = {AGB},
description = {Asymptontic Giant Branch. \\Part of the HR diagram where stars evolve off MS and into gaints}
}

\newglossaryentry{ac:AIC}{
name={AIC},
description={Accretion Induced Collaspe \\ When a WD reaches the \gls{chandrasekhar-limit} in a close binary}
}

\newglossaryentry{ac:BEER}{
name={BEER},
description={BEaming, Ellipsoidal, and Reflection/emission modulation \\ Method for detecing exoplants or blackholes based on variations in an observed star. See \gls{RelativisticBeaming}}  
}

\newglossaryentry{ac:BH-LS}{
name={BH-LS},
description={Black Hole w/Luminous companion}
}

\newglossaryentry{ac:DD}{
name={DD},
description={\textit{Double Degenerate}, donor as well as accretor are WDs}
}

\newglossaryentry{ac:GRBs}{
name={GRBs},
description={Gamma-ray Burst // Extremly bright high energy sources seen in other galaxies. Belived to be from supernova and superluminous supernova}
}

\newglossaryentry{ac:GW}{
name={gravtional wave},
description={Gravitational Waves \\ See section}
}

\newglossaryentry{ac:GWR}{
name={GWR},
description={gravitnal wave radiation.\\ Process of stars losing angular momentum through the radiation of gravitnal waves}
}

\newglossaryentry{ac:LVB}{
name = {LVB},
description = {luminos blue variables.\\ These are which \(T_{eff} > 20000\text{K}\) }
}

\newglossaryentry{AC:MAD}{
name={MAD},
description={Magnetically Arrested Disk // State of the magnetic field around a BH. Accurs when the grav field is equal to the grav force, leading to a torque on the system, slowing down the BHs spin}
}

\newglossaryentry{ac:MB}{
name={MB},
description={Magnetic Breaking. \\ Process whbere two stars ``couple'', causing a loss of angular momentum}
}

\newglossaryentry{ac:MSP}{
name={MSP},
description={Milisecond Pulsar. \\ A pulsar with a spin period \(\sim 30\)ms}
}

\newglossaryentry{ac:ONeMg}{
name={ONeMg},
description={Fill this in later hopefully. Pretty sure it just means Oxygen, Neon and Magnesium?}
}

\newglossaryentry{ac:PISN}{
name={PISN},
description={pair-instability supernova\\ Beleived to happen to stars of mass between 130-250, where their end of life SN are so energetic it leaves behind \textit{no compact object}. This means that theortiecally no BHs between 45-120 should be able to form directly from SN. This is called the \textbf{PISN black hole mass gap}}
}

\newglossaryentry{ac:RSG}{
name={RSG},
description={Red-supergiant \\ Supergaint stars with a spectral class of M or K  }
}

\newglossaryentry{ac:SD}{
name={SD},
description={\textit{Single Degenerate}, donor is a normal star, accretor is WD}
}

\newglossaryentry{ac:SMBH}{
name={SMBH},
description={Super-Massive Black Hole\\ Black hole with a mass \textit{greater} than 100,000 solar masses }
}

\newglossaryentry{ac:TDE}{
name={TDE},
description={Tidal Disruption Event \\ Event where a star passed to close to a BH and is violenty ripped apart, producing a brust of light}
}

\newglossaryentry{ac:TESS}{
name={TESS},
description={Transiting Expoplanet Survey Satelitte \\ satelitte dedicated to searching for exoplants via transit method, similar to kepler, albiet in a \textit{much} larger region.}
}

\newglossaryentry{ac:TI-SNe}{
name={Type I SNe},
description={A SNe \textbf{without} hydrogen in its spectra\\ Generally standard candles. They are thermonuclear explosions of carbon-oxygen WDs. See section(\ref{WD-SNe})}
}

\newglossaryentry{ac:TIb-SNe}{
name={Type Ib SNe},
description={A SNe \textbf{without} hydrogen and with helium in its spectra. \\ Caused by collaspe of the naked helium core star.}
}

\newglossaryentry{ac:TIc-SNe}{
name={Type Ic SNe},
description={A SNe \textbf{without} hydrogen or helium in its spectra. \\ A star where both the hydrogen and helium envelopes have been fully stripped.}
}

\newglossaryentry{ac:TII-SNe}{
name={Type II SNe},
description={A SNe \textbf{with} hydrogen in its spectra \\ generally found in galaxies with high star formation rate. Likely caused by core collaspe}
}

\newglossaryentry{ac:WNh}{
name={WNh},
description={Very massive stars with strong stellar winds, leading to spectra very similar to that of WRs, but also with hydrogen emission. These have ejected their outer shells of hydrogen, and show distinct He and/or C emission, buta also is still doing H fusion in the core}
}

\newglossaryentry{ac:WR-star}{
name={WR star},
description={Wolf-Rayet star. \\A helium star of mass They are genally so massive (typically more than \(\sim25M_\odot\)) that it sheds its hydrogen layer due to stellar wind. It may also shed its helium layer as well.}
}

\newglossaryentry{ac:ZAMS}{
name={ZAMS},
description={Zero age main sequence
This is a star which is has literally just started on the main seqeunce. Hence `zero-age'}
}

\newglossaryentry{algol-type}{
  name={Algol Type},
  description={Type of eclipsing binary with properties similar to the Algol system. It appears paradoxical because the more evolved star has a smaller mass, explained by mass transfer.}
}

\newglossaryentry{antibiotic-index}{
name={antibiotic index},
description={Also called a heart capacity ratio. A very very very simplified and abstract defenition is how much a gas will expand when heated. \url{https://en.wikipedia.org/wiki/Heat_capacity_ratio}}
}

\newglossaryentry{Barium-stars}{
name={Barium stars},
description={G and K type gaints with a `overabundance' of barium and other s-process elements \\Wide binaries with longer periods}
}

\newglossaryentry{Blue-stragglers}{
name={Blue stragglers},
description={}
}

\newglossaryentry{Case-A-RLO}{
name={Case A RLO},
description={RLO during donor hydrogen core burning (Meaning mainsequence) 
\cite{yungelsonElusiveHotStripped2024}}
}

\newglossaryentry{Case-B-RLO}{
name={Case B RLO},
description={This is where the donor star is \textit{post} hydrogen core burning. Ex. hydrogen \textit{shell} burning 
\cite{yungelsonElusiveHotStripped2024} \\
See \ref{Yungelson-case-b-rlo} for more info} 
}

\newglossaryentry{chandrasekhar-limit}{
name={Chandrasekhar Limit},
description={Maxiumum mass of a white dwarf, approx \(M \approx 1.4M_\odot\)\\ This is support be electron degeneracy pressure}
}

\newglossaryentry{collapser}{
name={Collapser},
description={Black hole formed for Core Collapse SNe, belived to be a gammaray source. See \ref{Collapsers}}
}

\newglossaryentry{Comptonization}{
name={Comptonization},
description={Process where hot electrons can boost low energy \textit{photons} up to x-ray energies. See \ref{https://www.astronomy.ohio-state.edu/ryden.1/ast822/week11.pdf} for more}
}

\newglossaryentry{consv-RLO}{
name={Conservative Roche lobe overflow},
description={RLO where the total mass and angular momentum remain constant. Is an example of Huangs \textit{slow mode}}
}

\newglossaryentry{Degenerate-matter}{
name={degenerate},
description={Matter which is under the effects of degeneracy from the \gls{pauli-exclusion-principle}. This is very commonly seen in neutron stars, as degeneracy pressure is what keeps them from collasping. \\ 
}
}

\newglossaryentry{eddington-limit}{
name={Eddington Limit},
description={\(\dot{M}_{Edd} \simeq 1.8 \times 10^{-8} M_\odot \mathrm{yr}^{-1}\) For NS \\ Maxium rate of mass transfer onto a NS or BH }
}

\newglossaryentry{eddington-lum-limit}{
name={Eddington (Luminosity) Limit},
description={The uper limit of the mass of a star, defined as \(3.2 \times 10^4 \left(\frac{M}{M_\odot}\right)L_\odot\)}
}

\newglossaryentry{edge-limit-detonation}{
name={edge limit detonation},
description={A WD SNe trigged by accreted H/He on the suface which sends a shockwave into the star, trigging runaway fusion.}
}

\newglossaryentry{even_modes}{
name={Even Modes},
description={(polar modes). A Pertubation which squash and stretch the sphere, akin to radial deformations. Important in spherical harmonics}
}

\newglossaryentry{hierarchical-merger}{
name={Hierarchical Merger},
description={When a one of the objects in a merger was already a product of a previous merger. I.e a second-generation (2G) BH merging with a 1G one.}
}

\newglossaryentry{kilonova}{
name={Kilonova},
description={A merger of either a NS+NS (DNS) binary or a NS+BH binary. Results in a bright signal resulting from the rapid decay the the NS material. Results in a peak brightness around 1000x that of a standard nova, hence the name. Likely a standard candle.}
}

\newglossaryentry{magnetic-breaking}{
name={magnetic breaking},
description={the process of a star magnetic field binding with the winds (or gas, etc), causing the stars spin to slow due to consv of ang momentum}
}

\newglossaryentry{ML-CircumDisk}{
name={Mass loss from a circumbinary disk}, %circumbinary disk?? i hardly know her!
description={Ejected mass from mass transfer/winds a ring orbiting the system (a circumbinary disk).\\ Refered to by Huang as an \textit{intermediate mode}. Due to tidal interactions these rings ``extract'' angular momentum from the system }
}

\newglossaryentry{natal-kick}{
name={Natal Kick},
description={A `kick' imparted on the object born from a SN from the SN itself. This is due to asymetric massloss, causing the star to be `pushed' in a direction}
}

\newglossaryentry{obs:Pan-STARRS}{
name={Pan-STARRS},
description={Panoramic Survey Telescope and Rapid Response System \\ Large observatory located in Hawaii used for surverying and rapid response. Big ass datasets}
}

\newglossaryentry{obs:Swift Observatory}{
name={Swift Observatory},
description={NASA ran space three telescope array observatory. Specifically setup for measuring \gls{ac:GRBs} and the x-ray + visable/ir afterglow}
}

\newglossaryentry{obs:XMM-Newton}{
name={XMM-Newton},
description={High Throughput X-ray Spectroscopy Mission or X-ray Multi-Mirror Mission \\ ESA launched and ran X-ray space observatory. Captures data in both visable and x-ray.}
}

\newglossaryentry{obs:ZTF}{
name={ZTF},
description={Zwicky Transient Facility\\ CalTech ran survery observatory in Palomar. Very large FOV, scans sky every 2 days.}
}

\newglossaryentry{odd_modes}{
name={Odd Modes},
description={(axial modes). A Pertubation which twists the sphere, linked to angular momentum-like distortion. Important in spherical harmonics}
}

\newglossaryentry{pauli-exclusion-principle}{
name={Pauli Exclusion Principle},
description={\fbox{See \ref{pauli-exclusion-principle} }}
}

\newglossaryentry{photon-gas}{
name={photon gas},
description={A `gas-like' collection of photons. This means that they have a tempature, pressure, and entropy. \\ They are most common in black-body equilibrums. \url{https://en.wikipedia.org/wiki/Photon_gas}}
}

\newglossaryentry{proper-motion}{
name={Proper Motion},
description={The motion of a star in the sky relative to more distant stars. Allows us understand the velocity of a star relative to the earth}
}

\newglossaryentry{Recylced-Pulsar}{
name={Recylced Pulsar},
description={A pulsar which obtained its rapid spin through accretion. Has weaker magnetic fields then newly formed NSs }
}

\newglossaryentry{RelativisticBeaming}{
name={Relativistic Beaming},
description={The process of an objects brightness being affected by its relative motion to earth, see\ref{sec:RelBeaming}. Note that this process is in conjuction \textit{with} dopller shift} 
}

\newglossaryentry{runaway-RLOF}{
name={runaway RLOF},
description={Unstable RLOF mass transfer which leads to eventual mergers}
}

\newglossaryentry{stellar-streams}{
name = {Stellar streams},
description = {Stars follwing a path away from a galaxy}
}

\newglossaryentry{surf-of-last-scatterting}{
name={Surface of last scattering},
description={Point looking deep into the universe where the universe becomes opaque. Also where the CMB is}
}

\newglossaryentry{thermal-timescale}{
name={Thermal Timescale},
description={}
}
